Using a Deep Autoencoder Model to Characterize Air Pollution

### 2021-09-18 paper-draft/paper.tex
Overhauled ae to include validation split, optimized run function

\begin{figure}[h]
\includegraphics[width=\textwidth]{/home/nicks/Documents/paper-draft/images/co-concentration-table.png}
    \caption{Carbon Monoxide Exposure Table, Parts Per Million (ppm)}
    \label{fig:co-exposure}
\end{figure}

@@

% pipeline
\begin{figure}[h]
\includegraphics[width=\textwidth, height=6cm]{/home/nicks/Documents/paper-draft/images/pipeline.png}
\caption{Data Pipeline}
\label{fig:pipeline}
\end{figure}

@@

\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=4cm]{/home/nicks/Documents/paper-draft/images/ae_all_dims.png} 
    \caption{Autoencoder Dimensionality Reduction}
    \label{fig:ae_dim_reduction}
\end{subfigure}% <- % sign must be here!
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=4cm]{/home/nicks/Documents/paper-draft/images/ae_all_dims.png}
    \caption{PCA Dimensionality Reduction}
    \label{fig:pca_dim_reduction}
\end{subfigure}

@@

\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=5cm]{/home/nicks/Documents/paper-draft/images/co_scatter_ae_wlist.png} 
    \caption{Outlier Cities}
    \label{fig:outliers}
\end{subfigure}% <- % sign must be here!
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=5cm]{/home/nicks/Documents/paper-draft/images/co_scatter_ae_large_cities.png}
    \caption{Densely Populated Cities}
    \label{fig:dense_cities}
\end{subfigure}

@@

% pipeline
\begin{figure}[h]
\includegraphics[width=\textwidth]{/home/nicks/Documents/paper-draft/images/corr_matrix_25.png}
\caption{Correlation Matrix}
\label{fig:matrix}
\end{figure}
\section{Discussion}

>>>>

\begin{figure}[h]
\includegraphics[width=\textwidth]{/home/nicks/github_repos/Pollution-Autoencoders/paper-draft/images/co-concentration-table.png}
    \caption{Carbon Monoxide Exposure Table, Parts Per Million (ppm)}
    \label{fig:co-exposure}
\end{figure}

@@

% pipeline
\begin{figure}[h]
\includegraphics[width=\textwidth, height=6cm]{/home/nicks/github_repos/Pollution-Autoencoders/paper-draft/images/pipeline.png}
\caption{Data Pipeline}
\label{fig:pipeline}
\end{figure}

@@

\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=4cm]{/home/nicks/github_repos/Pollution-Autoencoders/paper-draft/images/ae_all_dims.png} 
    \caption{Autoencoder Dimensionality Reduction}
    \label{fig:ae_dim_reduction}
\end{subfigure}% <- % sign must be here!
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=4cm]{/home/nicks/github_repos/Pollution-Autoencoders/spaper-draft/images/ae_all_dims.png}
    \caption{PCA Dimensionality Reduction}
    \label{fig:pca_dim_reduction}
\end{subfigure}

@@

\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=5cm]{/home/nicks/github_repos/Pollution-Autoencoders/paper-draft/images/co_scatter_ae_wlist.png} 
    \caption{Outlier Cities}
    \label{fig:outliers}
\end{subfigure}% <- % sign must be here!
\begin{subfigure}{0.5\textwidth}
    \includegraphics[width=1.1\linewidth, height=5cm]{/home/nicks/github_repos/Pollution-Autoencoders/paper-draft/images/co_scatter_ae_large_cities.png}
    \caption{Densely Populated Cities}
    \label{fig:dense_cities}
\end{subfigure}

@@

% pipeline
\begin{figure}[h]
\includegraphics[width=\textwidth]{/home/nicks/github_repos/Pollution-Autoencoders/paper-draft/images/corr_matrix_25.png}
\caption{Correlation Matrix}
\label{fig:matrix}
\end{figure}
\section{Discussion}
